
\documentclass[11pt,a4paper,roman]{moderncv}       
\moderncvstyle{banking}                          
\moderncvcolor{blue}                                
\nopagenumbers{}                                  

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}

\usepackage[scale=0.8]{geometry}
\usepackage{multicol}

\usepackage{import}
\name{Loveleen}{Amar}

\address{B-290 NH-3 RIHAND NAGAR NTPC COLONY}{SONEBHADRA}{UTTAR PRADESH(231223)}
  
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\setlength{\tabcolsep}{11pt}


\begin{document}
 
\makecvtitle
\vspace*{-23mm}

\begin{center}
\begin{tabular}{ c c c c }
  \faEnvelopeO\enspace loveleen242493@gmail.com & \faGithub\enspace github.com/loveleen123 &  \faMobile\enspace 9340070698\\  
\end{tabular}
\end{center}


\section{EDUCATION}
{\customcventry{(2017 - 2021)
}{International Institute Of Information Technology,Atal Nagar, Chhattisgarh}{Bachelor of Technology (B.Tech), Computer Science & Engineering }{SGPA(4rd sem: 9.3)}{}{}}
{\customcventry{2017}{ St. Josephs' School , Rihand Nagar  }{XII (Senior Secondary), Science, CBSE Board}{Percentage: 95.8}{}{}}


{\customcventry{2015}{St. Josephs' School , Rihand Nagar   }{X (Secondary),
CBSE Board}{CGPA:9.8}{}{}}

\section{KEY SKILLS}


\section{ACADEMIC PROJECTS}

{\customcvproject{Network Classification using Deep Learning Concept}{Jan-May 2019 }
{\begin{itemize}
  \item Will be able to classify different types of Internet Traffic classes.
  \item Concept Of CNN is being used.
\end{itemize}
}
}


{\customcvproject{Sentiment Analysis using Naive Bayes classifier}{June 2019 }
{\begin{itemize}
  \item this will be able to classify the sentiment of the user based on the text entered by him/her as positive/negative.
  \item Concept Of Naive Bayes is being used.
\end{itemize}
}
}

{\customcvproject{Hand written digit cleaning done using KNN- Classifier}{June 2019 }
{\begin{itemize}
  \item Dependent and independent both the variables are pixel values after applying the model the image of the digit is clear .
  \item K-Nearest Neighbors classifier has been used.
\end{itemize}
}
}

{\customcvproject{Training And Placement Website for IIIT Naya Raipur}{March- 2019 }
{\begin{itemize}
  \item It is Training And Placement Website for International Institute Of Information Technology Naya RAipur.
  \item Front end done usng HTML, CSS, Javascript, jQuery,Bootstrap.Backend done on PHP.
\end{itemize}
}
}




{\customcvproject{Audio Compression using MATLAB}{Oct 2018 - Dec 2018}
{\begin{itemize}
  \item This will compress the size of any audio file(like .wav, .audio, .mp3 etc). The
main function used here is the DCT and IDCT . But this will compress the file
to less extent so we further used bit rate concept too.
  \item link on github: github.com/loveleen123/AUDIO-COMPRESSOR
\end{itemize}
}
}

{\customcvproject{Semi-Autonomous Tractor model using Raspberry-pi}{Mar 2018 - May 2018
}
{\begin{itemize}
  \item This project was done with the help of R-pi. The tractor will move
autonomously without human interference.
  \item It will plough the feild and will stop autonomously when required.
\end{itemize}
}
}



{\customcvproject{Web-Development project: Gallery and Registration Page}{Mar 2018 - Mar 2018
}
{\begin{itemize}
  \item Basic Frontend Part- gallery and registration page using html , css,
bootstrap.
  \item link on github: github.com/loveleen123/WEB-DEV-Gallery--
\end{itemize}
}
}






{\customcvproject{Voice Control Wheel Chair Protocol Using Arduino
}{Oct 2017 - Dec 2017
}
{\begin{itemize}
  \item Based on the voice of the patient the wheel chair will move accordingly.The command where left ,right , forward, backward.
  \item The programming on arduino was done so as to move the chair according to the commands given.
\end{itemize}
}
}




\section{TRAINING AND EXPERIENCE}


{\customcventry{}{}{}{}{}
{\begin{itemize}
 \item HPE Summer training on Machine Learning and Deep Learning from Ardent Institute,Kolkata in June 2019
  \item  Currently working on Machine Learning algorithms,using
    udemy (Online course).Started
     Jan 2019 - Present
     Just a novice in this course, this course includes various complex machine learning theory, algorithms and coding libraries in a simple way in python.
  \item  Online course on Web Development on
  udemy.Started on
  Dec 2018 and presently working on that.
 Boot Camp on by Colt Steel.
 \item Worked for making Web page for TSOC(The Society Of Coders) of IIIT Naya Raipur.
 \item Worked in core team of Merchandiser and Curator of TNP (Training and Placement Cell) of IIIT Naya Raipur.
\end{itemize}
}
}


\section{POSITIONS OF RESPONSIBILITY}

{\customcventry{}{}{}{}{}
{\begin{itemize}
  \item  Senior Member of TSOC(The Society Of Coders) club of IIIT Naya Raipur.
  \item Core Team of TNP(Training and Placement Cell) of IIIT Naya Raipur.
  \item  Member in Website Designing team in Technovate 2017
 \item Volunteered in Hack D Unhacked',Central India's Largest Hackathon
(hackathon competition ) and Wolf Of Web Streets(web-designing event),
in our college fest Technovate 2017.
\item Member of the Front end development Team in TSOC club.
 \item Showcased and demonstrated the project "Voice Control Wheel Chair
Using Arduino" to various school students in ScientFic 2017 organised by IIIT Naya Raipur.
 \item Achieved the post of POWER ANGEL (Women Power Line) by Uttar
Pradesh Government
 \item School Vice Captain for Sashtri house (in 2015)
 \item School Captain for Sashtri house (in 2016)
\end{itemize}
}
}

\section{SKILLS AND KNOWLEDGE}

{\customcventry{}{}{}{}{}
{\begin{itemize}
  \item   LANGUAGES:C,C++,JAVA,PYTHON,JAVASCRIPT,JQUERY,HTML,CSS,BOOTSTRAP,SQL,NODEJS.
  \item  MACHINE LEARNING.
  \item  SOFTWARES: MATLAB,RASBERRY-PI,ARDUINO,NI-MULTISIM.
\end{itemize}
}
}









\section{AWARDS AND ACHIEVEMENTS}
\begin{minipage}{\maincolumnwidth}%
	\small{
    	\begin{itemize}
    	  
          \item School Topper in CBSE 12th Board.
          
          
          \item 1st position in 3D-Collage making competition held in JOSEPHEST at Allahabad
            \item 3rd position for Group-Creativity in Josephest.
          \item Best turnout award in parade.
          \item  Intra-School Badminton tournament Runner-up.
           \item 1st position in Techno-Cultural Fest of  IIITNR in Web-App Development event(Made Training and Placement website).
		\end{itemize}}%
\end{minipage}%
      
}

\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        


\end{document}


